```{r config, child="section_config.Rmd", message=FALSE, warning=FALSE, echo=FALSE}
```

```{r custom, echo=FALSE}
var_code <- "cu25"
var_meta <- metagci11[metagci11$code == var_code,]
var_prettynom <- var_meta[,2]
var_sides <- 5
var_cciso <- "NZL"
var_highlight <- "New Zealand"
```

## `r paste(var_meta[,2], var_meta[,1])`

**From Good Country Source Descriptions**:

**Description**: `r var_meta[,4]`

**Source**: `r var_meta[,5]`

**Treatment**: `r var_meta[,6]`

**Neighbouring Countries**:

```{r ranking, child="section_rank.Rmd", echo=FALSE}
```

`r neighbours`


```{r maingraph, child="section_maingraph.Rmd", dpi=270, width=7, height=5, echo=FALSE}
```

**My Interpretation and Opinions**:

Press Freedom also seems to have an association with GDP per capita, as contries with well off inhabitants are concentrated in the top 30% of GCI ranks.

New Zealand seems to have a very good rank for its GDP per capita (overall better than Canada and Germany, worse than Ireland and Belgium), so there would not seem to be much opportunity to improve in this area.

```{r child="section_config.Rmd", eval=TRUE, echo=TRUE, results = "hide", fig.keep="none"}
```

```{r custom, eval=FALSE, echo=TRUE}
```

```{r child="section_rank.Rmd", eval=TRUE, echo=TRUE, results = "hide", fig.keep="none"}
```

```{r child="section_maingraph.Rmd", eval=TRUE, echo=TRUE, results = "hide", fig.keep="none"}
```
