```{r config, child="section_config.Rmd", message=FALSE, warning=FALSE, echo=FALSE}
```

```{r custom, echo=FALSE}
var_code <- "ps31"
var_meta <- metagci11[metagci11$code == var_code,]
var_prettynom <- var_meta[,2]
var_sides <- 5
var_cciso <- "NZL"
var_highlight <- "New Zealand"
```

## `r paste(var_meta[,2], var_meta[,1])`

**From Good Country Source Descriptions**:

**Description**: `r var_meta[,4]`

**Source**: `r var_meta[,5]`

**Treatment**: `r var_meta[,6]`

**Neighbouring Countries**:

```{r ranking, child="section_rank.Rmd", echo=FALSE}
```

`r neighbours`


```{r maingraph, child="section_maingraph.Rmd", dpi=270, width=7, height=5, echo=FALSE}
```

**My Interpretation and Opinions**:

The measure of number of peacekeepers (in relation to size of economy) is highly sensitive to GDP per capita. Among countries that supply peace keepers, the number supplied decreases as GDP per capita increases.

New Zealand is in the better half of countries overall, the worse half of countries supplying peacekeepers, and the better half of what might be expected given the wealth of its inhabitants. The GCI range New Zealand is in places us a little better than Canada and Norway, and a bit worse than Belgium and China.

There would seem to be some room for improving New Zealands peacekeeping relative to other countries, but that needs to be caveated by economic confounders clearly in play.

```{r child="section_config.Rmd", eval=TRUE, echo=TRUE, results = "hide", fig.keep="none"}
```

```{r custom, eval=FALSE, echo=TRUE}
```

```{r child="section_rank.Rmd", eval=TRUE, echo=TRUE, results = "hide", fig.keep="none"}
```

```{r child="section_maingraph.Rmd", eval=TRUE, echo=TRUE, results = "hide", fig.keep="none"}
```
