```{r config, child="section_config.Rmd", message=FALSE, warning=FALSE, echo=FALSE}
```

```{r custom, echo=FALSE}
var_code <- "ps35"
var_meta <- metagci11[metagci11$code == var_code,]
var_prettynom <- var_meta[,2]
var_sides <- 5
var_cciso <- "NZL"
var_highlight <- "New Zealand"
```

## `r paste(var_meta[,2], var_meta[,1])`

**From Good Country Source Descriptions**:

**Description**: `r var_meta[,4]`

**Source**: `r var_meta[,5]`

**Treatment**: `r var_meta[,6]`

**Neighbouring Countries**:

```{r ranking, child="section_rank.Rmd", echo=FALSE}
```

`r neighbours`


```{r maingraph, child="section_maingraph.Rmd", dpi=270, width=7, height=5, echo=FALSE}
```

**My Interpretation and Opinions**:

There is a relationship between GDP per capita and Internet Security, and New Zealand is at the upper end of both raw ranks and the ranks in relation to wealth. So maybe we could improve a little with more effort, but we are well above average to start with so any reversion to the mean would bring us down.

```{r child="section_config.Rmd", eval=TRUE, echo=TRUE, results = "hide", fig.keep="none"}
```

```{r custom, eval=FALSE, echo=TRUE}
```

```{r child="section_rank.Rmd", eval=TRUE, echo=TRUE, results = "hide", fig.keep="none"}
```

```{r child="section_maingraph.Rmd", eval=TRUE, echo=TRUE, results = "hide", fig.keep="none"}
```
