```{r config, child="section_config.Rmd", message=FALSE, warning=FALSE, echo=FALSE}
```

```{r custom, echo=FALSE}
var_code <- "wo45"
var_meta <- metagci11[metagci11$code == var_code,]
var_prettynom <- var_meta[,2]
var_sides <- 5
var_cciso <- "NZL"
var_highlight <- "New Zealand"
```

## `r paste(var_meta[,2], var_meta[,1])`

**From Good Country Source Descriptions**:

**Description**: `r var_meta[,4]`

**Source**: `r var_meta[,5]`

**Treatment**: `r var_meta[,6]`

**Neighbouring Countries**:

```{r ranking, child="section_rank.Rmd", echo=FALSE}
```

`r neighbours`


```{r maingraph, child="section_maingraph.Rmd", dpi=270, width=7, height=5, echo=FALSE}
```

**My Interpretation and Opinions**:

UN treaties signed relates weakly to GDP per capita, as no wealthy countries show a large rejection of the UN.

Because this ranking is almost entirely made up of tied blocks, I suspect (without actually checking the data) that the differences between each block are a very small number of signed treaties. This in turn would mean that signing one treaty makes a large difference in rank, as it shifts a country into being tied among the next better block.

New Zealand, tied in the third block, would experience a big leap in GCI rank if it ratified another UN treaty.


```{r child="section_config.Rmd", eval=TRUE, echo=TRUE, results = "hide", fig.keep="none"}
```

```{r custom, eval=FALSE, echo=TRUE}
```

```{r child="section_rank.Rmd", eval=TRUE, echo=TRUE, results = "hide", fig.keep="none"}
```

```{r child="section_maingraph.Rmd", eval=TRUE, echo=TRUE, results = "hide", fig.keep="none"}
```
