```{r config, child="section_config.Rmd", message=FALSE, warning=FALSE, echo=FALSE}
```

```{r custom, echo=FALSE}
var_code <- "pe63"
var_meta <- metagci11[metagci11$code == var_code,]
var_prettynom <- var_meta[,2]
var_sides <- 5
var_cciso <- "NZL"
var_highlight <- "New Zealand"
```

## `r paste(var_meta[,2], var_meta[,1])`

**From Good Country Source Descriptions**:

**Description**: `r var_meta[,4]`

**Source**: `r var_meta[,5]`

**Treatment**: `r var_meta[,6]`

**Neighbouring Countries**:

```{r ranking, child="section_rank.Rmd", echo=FALSE}
```

`r neighbours`


```{r maingraph, child="section_maingraph.Rmd", dpi=270, width=7, height=5, echo=FALSE}
```

**My Interpretation and Opinions**:

The Fairtrade market size indicator is sensitive to GDP per capita in both an obvious and non-obvious way.

Mid range to wealthy countries dominate the best rankings, marking a clear division with lower wealth countries.

Less obviously, but just as important, only a small number of countries have a fair trade sector reported, and the presence of countries in the data is heavily weighted to wealthier countries. This creates a non response bias, giving the scores a very different rank to what they would have if there was a more complete data set.

New Zealand is in the top 10, but this is not a particularly good achievement in relation to the limited set of data present. The easiest way of improving New Zealand's rank in this area would be to include more countries.


```{r child="section_config.Rmd", eval=TRUE, echo=TRUE, results = "hide", fig.keep="none"}
```

```{r custom, eval=FALSE, echo=TRUE}
```

```{r child="section_rank.Rmd", eval=TRUE, echo=TRUE, results = "hide", fig.keep="none"}
```

```{r child="section_maingraph.Rmd", eval=TRUE, echo=TRUE, results = "hide", fig.keep="none"}
```
