```{r config, child="section_config.Rmd", message=FALSE, warning=FALSE, echo=FALSE}
```

```{r custom, echo=FALSE}
var_code <- "h_HealthWellbeing"
var_prettynom <- "Health & Wellbeing"
var_sides <- 5
var_cciso <- "NZL"
var_highlight <- "New Zealand"
```

# `r var_prettynom` - Aggregate Score

**Neighbouring Countries**:

```{r ranking, child="section_rank.Rmd", echo=FALSE}
```

`r neighbours`


```{r maingraph, child="section_maingraph.Rmd", dpi=270, width=7, height=5, echo=FALSE}
```

**My Interpretation and Opinions**:

The Health and Wellbeing aggregate category ranking is related to DP per capita in a similar way to other aggregates.

Much like some of the early aggregates, I personally think number of medical school graduates per capita is a figure worth exploring, as with a general world wide shortage of doctors it might be a use proxy for contempory contributions to health.

```{r child="section_config.Rmd", eval=TRUE, echo=TRUE, results = "hide", fig.keep="none"}
```

```{r custom, eval=FALSE, echo=TRUE}
```

```{r child="section_rank.Rmd", eval=TRUE, echo=TRUE, results = "hide", fig.keep="none"}
```

```{r child="section_maingraph.Rmd", eval=TRUE, echo=TRUE, results = "hide", fig.keep="none"}
```
