```{r config, child="section_config.Rmd", message=FALSE, warning=FALSE, echo=FALSE}
```

```{r custom, echo=FALSE}
var_code <- "hw74"
var_meta <- metagci11[metagci11$code == var_code,]
var_prettynom <- var_meta[,2]
var_sides <- 5
var_cciso <- "NZL"
var_highlight <- "New Zealand"
```

## `r paste(var_meta[,2], var_meta[,1])`

**From Good Country Source Descriptions**:

**Description**: `r var_meta[,4]`

**Source**: `r var_meta[,5]`

**Treatment**: `r var_meta[,6]`

**Neighbouring Countries**:

```{r ranking, child="section_rank.Rmd", echo=FALSE}
```

`r neighbours`


```{r maingraph, child="section_maingraph.Rmd", dpi=270, width=7, height=5, echo=FALSE}
```

**My Interpretation and Opinions**:

Humanitarian Aid (relative to the size of the economy) is related to the GDP per capita. As normal wealthy countries are in all the best ranks. 

New Zealand has a very good rank overall, and a very good rank for its wealth. So it is liekly difficult to improve much more given the position we are currently at.



```{r child="section_config.Rmd", eval=TRUE, echo=TRUE, results = "hide", fig.keep="none"}
```

```{r custom, eval=FALSE, echo=TRUE}
```

```{r child="section_rank.Rmd", eval=TRUE, echo=TRUE, results = "hide", fig.keep="none"}
```

```{r child="section_maingraph.Rmd", eval=TRUE, echo=TRUE, results = "hide", fig.keep="none"}
```
